---
title: "200_nivabase_urban_2022"
author: "DHJ"
date: "2023-11-05"
output: html_document
---

## Read data from Nivabase   
- Script 200_Nivabase_[program]_[year]     
- functions used   
    - get_stations_from_project_id  
    - get_specimens_from_stationdata   
    - get_biota_chemistry  
    - get_water_chemistry_from_stations  
    - get_sediment_chemistry_from_stations  
    
## 1. Setup  

### For filenames  
```{r}

program_year <- "Urban_2022"
sampling_year <- 2022

```

### Labware data  

```{r}

# dat_lab <- readRDS("Data/100_dat_lab_Milfersk_2022_2023-06-22.rds")

```


### Packages and functions  
```{r}

library_q <- function(...) suppressPackageStartupMessages(library(...))

devtools::install("../niRvana", upgrade = "never", quiet = TRUE)
library(niRvana)
library_q(dplyr)
library_q(purrr)
library_q(lubridate)
library_q(readxl)
library_q(ggplot2)
library_q(tidyr)
library_q(knitr)     # for kable
# library(fuzzyjoin)   # regex_full_join

source("010_functions.R")

knitr::opts_chunk$set(results = 'hold')

```


### Set up connection to Nivabasen on Oracle   

```{r}

con <- DBI::dbConnect(odbc::odbc(),
                      Driver = "/opt/conda/orahome/libsqora.so.12.1",
                      DBQ = "dbora-niva-prod01.niva.corp:1555/NIVABPRD",
                      UID = rstudioapi::showPrompt("Connect to Nivabasen", "Database username"),
                      PWD = rstudioapi::askForPassword("Nivabasen password"))


# Tell niRvana that it should use this connection  
options(use_existing_connection = TRUE)

```


## 2.  Check existing NIVAbasen data    

```{r}

df_projects <- get_projects()   

# df_stations <- get_stations_from_project("MILFERSK", exact = FALSE)
df_stations <- get_stations_from_project("urban", exact = FALSE)
df_stations <- get_stations_from_project("Urban fjord", exact = TRUE)

nrow(df_stations)

```

#### Get all data    

* NOTE: No water - as stations haven't been defined for the water samples (see script 100)   

```{r}

# 
## Biota samples
#

df_specimens <- get_specimens_from_stationdata(df_stations, years = sampling_year)
message("No. of specimens, biota: ", nrow(df_specimens))
dat_nb_biota <- get_biota_chemistry(sampling_year, df_specimens, df_stations, report_samples = TRUE)

dat_nb_biota <- dat_nb_biota %>%
  mutate(Year = year(SAMPLE_DATE))

# 421  

#
## Water samples  
#

df_samples_water <- get_nivabase_selection(
  "*",
  "WATER_SAMPLES",
  "STATION_ID",
  df_stations$STATION_ID
)
message("No. of samples, water: ", nrow(df_samples_water))

# Adds "SAMPLE_TYPE", "SAMPLE_NUMBER", "DESCRIPTION" and "n_labware" from Labware

# debugonce(get_water_chemistry_from_stations)
dat_nb_water <- get_water_chemistry_from_stations(unique(df_samples_water$STATION_ID), sampling_year)
message("No. of measurements, water: ", nrow(dat_nb_water))

df_samples_sediment <- get_nivabase_selection(
  "*",
  "SEDIMENT_SAMPLES",
  "STATION_ID",
  df_stations$STATION_ID
)
message("No. of samples, sediment: ", nrow(df_samples_sediment))

dat_nb_sediment <- get_sediment_chemistry_from_stations(df_stations$STATION_ID, years = sampling_year)

dat_nb_sediment_methods <- get_chemistry_methods(method_id = unique(dat_nb_sediment$METHOD_ID))

dat_nb_sediment <- dat_nb_sediment %>%
  left_join(dat_nb_sediment_methods, by = "METHOD_ID") %>%
  mutate(Year = year(SAMPLE_DATE)) 

```

### Check biota data  

#### Number of individuals per station  
```{r}

dat_nb_biota %>%
  distinct(LATIN_NAME, STATION_CODE, SAMPLE_NO) %>%
  count(LATIN_NAME, STATION_CODE)

```

#### Number of measurements per species    
```{r}

dat_nb_biota %>%
  distinct(NAME, LATIN_NAME, SAMPLE_NO) %>%
  count(NAME, LATIN_NAME, name = "number_ind") %>%
  pivot_wider(names_from = LATIN_NAME, values_from = number_ind)

```

## 3. Seal samples  

* Special for this year: used old seal samples    

### Check LIMS  

```{r}

df_samples_seal <- get_nivabase_data(paste(
  "select * from NIVADATABASE.LABWARE_CHECK_SAMPLE",
  "where PROSJEKT like '%urban%'",
  "and SPECIES = 'Phoca vitulina'"))

# Tissues
xtabs(~TISSUE, df_samples_seal)

# Dates
xtabs(~SAMPLED_DATE, df_samples_seal)
xtabs(~RECD_DATE, df_samples_seal)

# Tissues
xtabs(~AQUAMONITOR_CODE, df_samples_seal)

```

### In Nivabasen  

```{r}

# Get all UB stations where STATION_CODE contains 'Sel' 
df_stations_seal <- df_stations %>%
  filter(grepl("Sel", STATION_CODE))

# Get specimens from 2021 on these stations
df_specimens <- get_specimens_from_stationdata(df_stations_seal, years = 2021)
message("No. of specimens, biota: ", nrow(df_specimens))
dat_nb_biota <- get_biota_chemistry(2021, df_specimens, df_stations_seal, 
                                    report_samples = TRUE, months_second_year = 0)

dat_nb_biota <- dat_nb_biota %>%
  mutate(Year = year(SAMPLE_DATE))


```


### Check biota data  

#### Number of individuals per station  
```{r}

dat_nb_biota %>%
  distinct(LATIN_NAME, STATION_CODE, SAMPLE_NO) %>%
  count(LATIN_NAME, STATION_CODE)

```

#### Number of measurements per species    
```{r}

dat_nb_biota %>%
  distinct(NAME, LATIN_NAME, SAMPLE_NO) %>%
  count(NAME, LATIN_NAME, name = "number_ind") %>%
  pivot_wider(names_from = LATIN_NAME, values_from = number_ind)

```
