---
title: "020_Oracle_using_niRvana"
author: "DHJ"
date: "2023-10-26"
output: 
  html_document:
    keep_md: true
    toc: true  
    toc_float: true
params:
  oracleuser: 
    label: "NIVA initials (3 capital letters)"
    value: "DHJ"
    input: text
  oraclepass: 
    label: "Oracle password"
    value: ""
    input: password
---


```{r}

library2 <- function(...) suppressPackageStartupMessages(library(...))

library2(dbplyr)
library2(dplyr)
library2(lubridate)
library2(ggplot2)
library2(stringr)
# devtools::install_github("NivaNorge/niRvana")
devtools::install("../niRvana", upgrade = "never")
library(niRvana)

```


## Set up Oracle connection   

- If interactive usage (running chunk by chunk), you will be asked for user/password   
- If you want to knit file, use "Knit with Parameters..." from the pull-down menu next to the Knit button  

```{r}

if (interactive()){
  con <- DBI::dbConnect(odbc::odbc(),
                      Driver = "/opt/conda/orahome/libsqora.so.12.1",
                      DBQ = "dbora-niva-prod01.niva.corp:1555/NIVABPRD",
                      UID = rstudioapi::showPrompt("Connect to Nivabasen", "Database username"),
                      PWD = rstudioapi::askForPassword("Nivabasen password"))
} else {
  con <- DBI::dbConnect(odbc::odbc(),
                        Driver = "/opt/conda/orahome/libsqora.so.12.1",
                        DBQ = "dbora-niva-prod01.niva.corp:1555/NIVABPRD",
                        UID = params$oracleuser,
                        PWD = params$oraclepass)
}


# After this we should tell niRvana that it should ues an existing connection  
#   options(use_existing_connection = TRUE)
# For demonstration, we don't do tha now  

```


## Test niRvana  

### Try default  

Results i n th error `there is no package called ‘keyring’` 

```{r}

# Define sql sentence
sql <- "select METHOD_ID, NAME, UNIT, BASIS_ID from NIVADATABASE.METHOD_DEFINITIONS where rownum < 5"

# debugonce(get_nivabase_data)
df_methods1 <- get_nivabase_data(sql)

```

### By setting use_existing_connection = TRUE  

Should work 

```{r}

df_methods2 <- get_nivabase_data(sql, use_existing_connection = TRUE)

```

### By setting the option 'use_existing_connection' to TRUE   

- The only alternative if we are going to use most functions in niRvana  

```{r}

options(use_existing_connection = TRUE)
df_methods3 <- get_nivabase_data(sql)

```

## Bigger test  

### Get data  
```{r}

# from ?get_biota_chemistry

# Get a list of projects
df_projects <- get_projects()   # we call it 'df_projects' (the default name)

# Get a list of stations
df1_stations <- get_stations_from_project("CEMP_Biota", ignore.case = FALSE)

# Get specimens collected at these stations 

# Speciemns for all years .- very slow on the hub (1-2 mins)
# df2_specimens_allyrs <- get_specimens_from_stationdata(df1_stations, )

df2_specimens <- get_specimens_from_stationdata(df1_stations, years = 2016)

# Get data frame of chemical results (30 seconds or so)
df_2016 <- get_biota_chemistry(
  years = 2016,
  specimendata = df2_specimens,
  stationdata = df1_stations,
  report_samples = TRUE)


```
### Test plot  

```{r}

ggplot(
  df_2016 %>% filter(NAME %in% "PCB 52" & LATIN_NAME %in% "Mytilus edulis"),
  aes(x = paste(STATION_CODE, STATION_NAME), y = VALUE, color = is.na(FLAG1))
) + 
  geom_point() +
  theme(axis.text.x = element_text(hjust = 0, angle = -45))

```

